Outputs from time slice analyses

### 2017-12-04 analyses/04-stats.Rmd
Added extinction tests

```{r, eval = TRUE, message = FALSE}
library(tidyverse)
library(broom)
```

@@

```{r}
out1 <- readRDS(file = paste0("../outputs/age.", slug, ".Rda"))
out2 <- readRDS(file = paste0("../outputs/epoch.", slug, ".Rda"))
```
Make the tables
```{r, eval = TRUE, echo = FALSE}
# Ages
knitr::kable(out1$results$stratigraphy, caption = "Disparity per stratigraphic age: unequal time bins and non-equidistant time slices")
knitr::kable(out1$results$duration, caption = "Disparity per average stratigraphic time: equal time bins and equidistant time slices based on the median stratigraphic age duration")
knitr::kable(out1$results$number, caption = "Disparity per average stratigraphic time: equal time bins and equidistant time slices based on the number of stratigraphic ages")

@@

>>>>

```{r, eval = TRUE, message = FALSE}
library(tidyverse)
library(broom)
library(dispRity)
```

@@

```{r}
out1 <- readRDS(file = paste0("../outputs/age.", slug, ".Rda"))
out2 <- readRDS(file = paste0("../outputs/epoch.", slug, ".Rda"))
```
Make the tables

```{r, eval = TRUE, echo = FALSE}
# Ages
knitr::kable(out1$results$stratigraphy, caption = "Disparity per stratigraphic age: unequal time bins and non-equidistant time slices")
knitr::kable(out1$results$duration, caption = "Disparity per average stratigraphic time: equal time bins and equidistant time slices based on the median stratigraphic age duration")
knitr::kable(out1$results$number, caption = "Disparity per average stratigraphic time: equal time bins and equidistant time slices based on the number of stratigraphic ages")

@@

Extinction effect
----------

Here we can test the effect of mass extinction on the different methods with the different models (for each dataset!).
The way to test the extinction effect is a referential wilcoxon test.#' @param as.list \code{logical}, whether to output the results as a list for \code{\link{test.dispRity}} (\code{TRUE}) or not (\code{FALSE} - default).

In other words, we compare the bins/slice just before the extinction event to the three ones just after (to account for an eventual lag effect).

Set the slug:

```{r}
slug <- "Beck2014" ; extinction <- 66.0
# slug <- "Brusatte2014"; extinction <- 66.0
# slug <- "Bapst2016"; extinction <- 66.0
# slug <- "bears"; extinction <- NA
# slug <- "Wright2017"; extinction <- 443.0
```

Measure differences in disparity:

```{r}
## Get the extinction times (ages)
ext_time_strat_age <- lapply(out1$objects$stratigraphy, extinction.subsets, extinction = extinction, lag = 3, as.list = TRUE)
ext_time_durat_age <- lapply(out1$objects$duration, extinction.subsets, extinction = extinction, lag = 3, as.list = TRUE)
ext_time_numbe_age <- lapply(out1$objects$number, extinction.subsets, extinction = extinction, lag = 3, as.list = TRUE)

## Get the extinction times (epochs)
ext_time_strat_epo <- lapply(out2$objects$stratigraphy, extinction.subsets, extinction = extinction, lag = 3, as.list = TRUE)
ext_time_durat_epo <- lapply(out2$objects$duration, extinction.subsets, extinction = extinction, lag = 3, as.list = TRUE)
ext_time_numbe_epo <- lapply(out2$objects$number, extinction.subsets, extinction = extinction, lag = 3, as.list = TRUE)

## Test the effect of extinctions
mapply.test <- function(data, times, test = wilcox.test, correction = "bonferroni") {
  test <- try(output <- test.dispRity(data, test = test, comparisons = times, correction = correction), silent = TRUE)
  if(class(test) == "try-error") {

    ## Create an NA list
    comparison_names <- unlist(lapply(times, function(time, data) paste(names(data$subsets)[time], collapse = " : "), data))
    p_value <- statistic <- data.frame(rep(NA, 3), row.names = comparison_names)
    colnames(statistic) <- "statistic: W"
    colnames(p_value) <- "p.value"

    return(list(statistic, p_value))
  } else {
    return(output)
  }
}

## Applying the tests (ages)
test_strat_age <- mapply(mapply.test, out1$objects$stratigraphy, ext_time_strat_age, SIMPLIFY = FALSE)
test_durat_age <- mapply(mapply.test, out1$objects$duration, ext_time_durat_age, SIMPLIFY = FALSE)
test_numbe_age <- mapply(mapply.test, out1$objects$number, ext_time_numbe_age, SIMPLIFY = FALSE)

## Applying the tests (epochs)
test_strat_epo <- mapply(mapply.test, out2$objects$stratigraphy, ext_time_strat_epo, SIMPLIFY = FALSE)
test_durat_epo <- mapply(mapply.test, out2$objects$duration, ext_time_durat_epo, SIMPLIFY = FALSE)
test_numbe_epo <- mapply(mapply.test, out2$objects$number, ext_time_numbe_epo, SIMPLIFY = FALSE)

## Combining the tests into tables
wrap.up.results <- function(results, type, method) {
  results <- data.frame(matrix(unlist(results), ncol = 6, byrow = TRUE))
  ## Adding the models
  results <- cbind(c("bins", "acctran", "deltran", "random", "proximity", "punctuated", "gradual"),results)
  ## Adding the type and method
  results <- cbind(matrix(c(rep(type, 7), rep(method, 7)), ncol = 2), results)
  ## Adding the column names
  colnames(results) <- c("type", "method", "model", "e:1(W)", "e:2(W)", "e:3(W)", "e:1(p)", "e:2(p)", "e:3(p)")
  return(results)
}

## Combining the results
result <- wrap.up.results(test_strat_age, "age", "stratigraphy")
result <- rbind(result, wrap.up.results(test_durat_age, "age", "duration"))
result <- rbind(result, wrap.up.results(test_numbe_age, "age", "number"))
result <- rbind(result, wrap.up.results(test_strat_epo, "epoch", "stratigraphy"))
result <- rbind(result, wrap.up.results(test_durat_epo, "epoch", "duration"))
result <- rbind(result, wrap.up.results(test_numbe_epo, "epoch", "number"))

## Significant results
result <- cbind(results, apply(result[,7:9], 2, function(col) ifelse(col < 0.05, TRUE, FALSE)))

## Print the table
knitr::kable(result)
```
